Geometric models reveal the hidden structure of conceptual knowledge

### 2023-01-20 paper/main.tex
🤦
added sliding window figure

Participants began the main experiment by answering a battery of 13 randomly
selected questions (chosen from the full set of 39). Then they watched the
\textit{The Four Fundamental Forces} video. Next, they answered a second set of
13 questions (chosen at random from the remaining 20 questions). Fourth,
participants watch the \textit{Birth of Stars} video, and finally they answered
the remaining 13 questions. Our experimental procedure is diagramed in
Figure~\ref{fig:experiment}. We used the experiment to develop and test our
computational framework for estimating knowledge and learning maps.

@@

>>>>

Participants began the main experiment by answering a battery of 13 randomly
selected questions (chosen from the full set of 39). Then they watched the
\textit{The Four Fundamental Forces} video. Next, they answered a second set of
13 questions (chosen at random from the remaining 26 questions). Fourth,
participants watch the \textit{Birth of Stars} video, and finally they answered
the remaining 13 questions. Our experimental procedure is diagramed in
Figure~\ref{fig:experiment}. We used the experiment to develop and test our
computational framework for estimating knowledge and learning maps.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/sliding_windows}

\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A.
Building a document pool from sliding windows of text.} We decompose each
video's transcript into a series of overlapping sliding windows. The set of
transcript snippets (across all windows) may be treated as a set of
``documents'' for training a text embedding model. After training a text
embedding model using the two videos' sliding windows, along with the text from
each question in our pool (Tab.~\questions), } we construct ``trajectories''
through text embedding space by joining the embedding coordinates of successive
sliding windows from each video. \textbf{B. Embedding multiple videos and
questions.} Applying the same text embedding approach to each video, along with
the text of each question, results in one trajectory per video and one
embedding coordinate (dot) per question (blue: Four Fundamental Forces; green:
Birth of Stars; pink: general physics knowledge).}

\label{fig:sliding-windows}
\end{figure}

\subsubsection*{Estimating dynamic knowledge traces}
